The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete v0.3

### 2014-01-11 main/scratch.tex
more octopus roll diagrams

\documentclass{robinminion}

@@

\newcommand\octorollA{

@@

		\draw (e)--(v);\draw (d)--(v);
		\draw[big>,bend right=10] (e1) to (a);  \draw[big>,bend right=20] (e2) to (a);  \draw[big>, bend right=30] (e3) to (a);

@@

		\draw (e)--(v);
	\SWITCH{#1}{1}{\draw (d)--(v);}\DEFAULT{\draw (d)--(a1a);}

@@

		\draw (e)--(v); \draw (d)--(a1a);

@@

		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v1);  \draw[big>, bend left=15] (e3) to (v2);

@@

	\node[big_] (d2) at (-6.25,4) {};
	\draw (-4,4) node[big_] (d3a) {} -- (-3,4) node[bullet] (d3b) {};

@@

		\draw (e)--(v); \draw (d)--(a1a);
		\draw[bend right=15] (d3b) to (v2);
		\draw[big>,bend left=20] (d3a) to (a1);
		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v1);  \draw[big>, bend left=15] (e3) to (v2);

@@

%\octorollA
%\vskip80pt
%\octorollB1
%\vskip80pt
%\octorollB2
%\vskip80pt
%\octorollB3
%\vskip80pt

\octorollC

\vskip80pt

\octorollD

\vskip80pt

%\octorollE

@@

%\newcommand\octorollC{
%  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
%	\node[circ] (a1a) at (0,1.5) {}; \node[big1] (a1) at (-2,0) {}; \node[big1] (a2) at (0,0) {}; \node[big1] (a3) at (2,0) {};
%	\draw (-9  ,4) node[bullet] (d1a) {} -- (-8  ,4) node[big_] (d1) {};
%	\draw (-6.5,4) node[bullet] (d2a) {} -- (-5.5,4) node[big_] (d2) {};
%	\draw (-4  ,4) node[bullet] (d3a) {} -- (-3  ,4) node[big_] (d3) {};
%	\draw[rounded corners] (-10,3) rectangle (-2,5);
%	\draw (-2,4)--(-1,4) node[bullet] (d) {};
%	\draw ( 3  ,4) node[bullet] (e1a) {} -- ( 4  ,4) node[big_] (e1) {};
%	\draw ( 5.5,4) node[bullet] (e2a) {} -- ( 6.5,4) node[big_] (e2) {};
%	\draw ( 8  ,4) node[bullet] (e3a) {} -- ( 9  ,4) node[big_] (e3) {};
%	\draw[rounded corners] (10,3) rectangle (2,5);
%	\draw (2,4)--(1,4) node[bullet] (e) {};
%	\node[circ] (v1a) at (-4,8); \node[big1] (v1b) at (-3,8) {}; \node[big1] (v1c) at (-1.5,8) {};
%	\node[big1] (v2) at  ( 2.5,8) {}; \node[big1] (v2) at ( 2.5,8) {};
%	\draw[rounded corners] (-4.5,7) rectangle (-0.5,9);
%	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
%	\draw (-0.5,8)--(0.5,8);
%	\node[circ] (v) at (0,6) {};
%	%
%	\begin{scope}[thepink,->]
%		\draw (e)--(v);\draw (d)--(v);
%		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
%		\draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e2a) to (a1a); \draw[bend right=15] (e3a) to (a1a); 
%		\draw[big>,bend right=20] (e1) to (a1);  \draw[big>,bend right=20] (e2) to (a2);  \draw[big>, bend right=20] (e3) to (a3);
%	\end{scope}
%  \end{tikzpicture}
%}

>>>>

\documentclass{beamer}

@@

\newcommand\octorollA[1]{

@@

		\draw[bend left=15] (e) to (v);\draw[bend right=15] (d) to (v);
	{1}{\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
		\draw[big>,bend right=10] (e1) to (a);  \draw[big>,bend right=20] (e2) to (a);  \draw[big>, bend right=30] (e3) to (a);}
	{2}{\draw[big>,bend left] (d1) to (a); \draw[big>,bend left=20] (d2) to (a); \draw[big>, bend left=20] (d3) to (a);
		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v2);  \draw[big>, bend left=15] (e3) to (v2);}
	\DEFAULT{}

@@

		\draw[bend left=15] (e) to (v);
	\SWITCH{#1}{1}{\draw[bend right=15] (d) to (v);}\DEFAULT{\draw[bend left=15] (d) to (a1a);}

@@

		\draw[bend left=15] (e) to (v); \draw[bend left=15] (d) to (a1a);

@@

		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v2);  \draw[big>, bend left=15] (e3) to (v2);

@@

	\draw (-6,4) node[big_] (d2a) {} -- (-5,4) node[bullet] (d2b) {};

@@

		\draw[bend left=15] (e) to (v); \draw[bend left=15] (d) to (a1a);
		\draw[bend right=15] (d2b) to (v1);
		\draw[big>,bend left] (d1) to (a1); \draw[big>,bend left=20] (d2a) to (a1); \draw[big>,bend left=20] (d3) to (a1);
		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v2);  \draw[big>, bend left=15] (e3) to (v2);

@@

\newcommand\octorollE[1]{
  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\node[big1] (a1) at (0,0) {}; \node[circ] (a1a) at (0,2) {};
	\node[big_] (d1) at (-8.5,4) {};
	\draw (-6,4) node[big_] (d2a) {} -- (-5,4) node[bullet] (d2b) {};
	\node[big_] (d3) at (-3.5,4) {};
	\draw[rounded corners] (-10,3) rectangle (-2,5);
	\draw (-2,4)--(-1,4) node[bullet] (d) {};
	\draw (2.75,4) node[bullet] (e1a) {} -- (3.5,4) node[bullet] (e1b) {} -- (4.5,4) node[big_] (e1c) {};
	\node[big_] (e2) at ( 6.5,4) {};
	\node[big_] (e3) at ( 8.5,4) {};
	\draw[rounded corners] (10,3) rectangle (2,5);
	\draw (2,4)--(1,4) node[bullet] (e) {};
	\node[circ] (v1a) at (-3.25,8) {}; \node[circ] (v1b) at (-2.5,8) {}; \node[big1] (v1c) at (-1.5,8) {};
	\node[big1] (v2) at ( 2,8) {};
	\draw[rounded corners] (-4,7) rectangle (-0.5,9);
	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
	\draw (-0.5,8)--(0.5,8);
	\node[circ] (v) at (0,6) {};
	%
	\begin{scope}[thepink,->]
		\draw[bend left=15] (e) to (v);
	\SWITCH{#1}
	{1}{
		\draw[bend left=15] (d) to (a1a);
		\draw[bend right=15] (d2b) to (v1a); \draw[bend right=15] (e1a) to (v1a); \draw[bend left=10] (e1b) to (v1b);
		}
	{2}{
		\draw[bend left=15] (d) to (a1a);
		\draw[bend right=15] (d2b) to (v1a); \draw[bend right=15] (e1a) to (a1a); \draw[bend left=10] (e1b) to (v1b);
		}
	{3}{
		\draw[bend right=15] (d) to (v1b);
		\draw[bend right=15] (d2b) to (v1a); \draw[bend right=15] (e1a) to (a1a); \draw[bend left=10] (e1b) to (v1b);
		}
	{4}{
		\draw[bend right=15] (d) to (v1b);
		\draw[bend right=15] (d2b) to (v1a); \draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e1b) to (v1a);
		}
	{5}{
		\draw[bend right=15] (d) to (v1b);
		\draw[bend left=25] (d2b) to (a1a); \draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e1b) to (v1a);
		}
	{6}{
		\draw[bend right=15] (d) to (v1b);
		\draw[bend left=25] (d2b) to (a1a); \draw[bend left=15] (e1a) to (v1b); \draw[bend right=15] (e1b) to (v1a);
		}
	{7}{
		\draw[bend right=15] (d) to (v);
		\draw[bend left=25] (d2b) to (a1a); \draw[bend left=15] (e1a) to (v1b); \draw[bend right=15] (e1b) to (v1a);
		}
	\DEFAULT{}
		\draw[big>,bend left] (d1) to (a1); \draw[big>,bend left=20] (d2a) to (a1); \draw[big>,bend left=20] (d3) to (a1);
		\draw[big>,bend left=15] (e1c) to (v1c);  \draw[big>,bend left=15] (e2) to (v2);  \draw[big>, bend left=15] (e3) to (v2);
	\end{scope}
  \end{tikzpicture}
}

\begin{frame}
	\octorollA1
\end{frame}

\begin{frame}
	\octorollB1
\end{frame}

\begin{frame}
	\octorollB2
\end{frame}

\begin{frame}
	\octorollB3
\end{frame}

\begin{frame}
	\octorollC
\end{frame}

\begin{frame}
	\octorollD
\end{frame}

\begin{frame}
	\octorollE1
\end{frame}

\begin{frame}
	\octorollE2
\end{frame}

\begin{frame}
	\octorollE3
\end{frame}

\begin{frame}
	\octorollE4
\end{frame}

\begin{frame}
	\octorollE5
\end{frame}

\begin{frame}
	\octorollE6
\end{frame}

\begin{frame}
	\octorollE7
\end{frame}

\begin{frame}
	\octorollA2
\end{frame}

@@

%\newcommand\octorollC{
%  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
%	\node[circ] (a1a) at (0,1.5) {}; \node[big1] (a1) at (-2,0) {}; \node[big1] (a2) at (0,0) {}; \node[big1] (a3) at (2,0) {};
%	\draw (-9  ,4) node[bullet] (d1a) {} -- (-8  ,4) node[big_] (d1) {};
%	\draw (-6.5,4) node[bullet] (d2a) {} -- (-5.5,4) node[big_] (d2) {};
%	\draw (-4  ,4) node[bullet] (d3a) {} -- (-3  ,4) node[big_] (d3) {};
%	\draw[rounded corners] (-10,3) rectangle (-2,5);
%	\draw (-2,4)--(-1,4) node[bullet] (d) {};
%	\draw ( 3  ,4) node[bullet] (e1a) {} -- ( 4  ,4) node[big_] (e1) {};
%	\draw ( 5.5,4) node[bullet] (e2a) {} -- ( 6.5,4) node[big_] (e2) {};
%	\draw ( 8  ,4) node[bullet] (e3a) {} -- ( 9  ,4) node[big_] (e3) {};
%	\draw[rounded corners] (10,3) rectangle (2,5);
%	\draw (2,4)--(1,4) node[bullet] (e) {};
%	\node[circ] (v1a) at (-4,8); \node[big1] (v1b) at (-3,8) {}; \node[big1] (v1c) at (-1.5,8) {};
%	\node[big1] (v2) at  ( 2.5,8) {}; \node[big1] (v2) at ( 2.5,8) {};
%	\draw[rounded corners] (-4.5,7) rectangle (-0.5,9);
%	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
%	\draw (-0.5,8)--(0.5,8);
%	\node[circ] (v) at (0,6) {};
%	%
%	\begin{scope}[thepink,->]
%		\draw[bend left=15] (e) to (v);\draw[bend right=15] (d) to (v);
%		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
%		\draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e2a) to (a1a); \draw[bend right=15] (e3a) to (a1a); 
%		\draw[big>,bend right=20] (e1) to (a1);  \draw[big>,bend right=20] (e2) to (a2);  \draw[big>, bend right=20] (e3) to (a3);
%	\end{scope}
%  \end{tikzpicture}
%}
